---
title: "Economics in R - Data of Macroeconomics"
author: "Hyundo Im"
date: "May 30 2017"
output:
  pdf_document: default
  html_document: default
---

# Measuring the Value of Economic Activity: Gross Domestic Product

__Gross Domestic Product__, or GDP, is considered the best measure of performances of the economy.
There are two ways to view GDP:
  1. view GDP as the total income of everyone in the economy
  2. the total expenditure on the economy's output of goods and services.

## Income, Expenditure, and the Circular Flow
* What is a flow?
  + Economists distinguish two kinds of quantity variables
    + Stock: a quantity measured at a given point in time
    + Flow: a quantity measured per unit of time.
  + Examples of Stock and Flow
    + A person's wealth is a tcok and his income and expenditure are flows
    + The number of unemployed people is a stock, the number of people losing their jobs is a flow
    + The amount of capital in the economy is a stock, the amount of investment is a flow

## Rules for Computing GDP
Definition of GDP again: _the market value of all final goods and services produced within an economy in a given period of time._

#### <span style = "color:red"> Used goods are not included in GDP </span>

#### <span style = "color:red"> Inventories that are produced in one year are only considered the part of GDP of that year no matter when it is sold </span>

#### <span style = "color:red"> Intermediate goods and value added are not included in GDP </span>

#### <span style = "color:red"> Housing services and other imputations are complicated... </span>

## Real GDP and Nominal GDP
Nominal GDP: the value of goods and services measured at current prices.
Real GDP: the value of good and services measured using a constant set of prices.

### <span style = "color:red"> Computing Real GDP </span>
Real GDP is measured with the price of _base year_.
EX) Suppose the base year is 2014.

Real GDP$_{2014} = Price_{2014} \times Quantity_{2014}$

Real GDP$_{2015} = Price_{2014} \times Quantity_{2015}$

Real GDP$_{2016} = Price_{2014} \times Quantity_{2016}$

## The GDP Deflator
GDP Deflator: also called _implicit price deflator for GDP_, is the ratio of nominal GDP to Real GDP

<center><h4> GDP Deflator = $\frac{Nominal GDP}{Real GDP}$ </h4></center>

We can rewrite as:
<center><h4> Real GDP = $\frac{Nominal GDP}{GDP Deflator}$ </h4></center>

__Let's take a look at GDP
```{r message=FALSE}
library(Quandl)
library(quantmod)
#Quandl.search("GDP Korea")
KOR_GDP<-Quandl("OECD/MEI_CLI_LORSGPTD_KOR_M",type = "xts")
plot(KOR_GDP,type="l",main="Korea's GDP(Normalized), 100= September 2010")
```

## The Components of Expenditure
The national income accounts divide GDP into four broad categories of spending:
* Consumption (C)
* Investment (I)
* Government Purchases (G)
* Net Exports (NX)
We can write GDP as:
<center><h4> Y = C + I + G + NX </h4></center>

This equation is called the __national income accounts identity__

__Consumption__ : goods and services bought by households

__Investment__ : goods bought for future use. Investment is also divided into three subcategories:
  1. Business fixed investment: purchase of new plant and equipment by firms
  2. Residential investment: the purchase of new housing by households and landlords.
  3. Inventory investment: the increase in firms' inventories of goods
  
__Government Purchases__ : goods and services bought by federal, state, and local governments.

__Net Exports__ : the value of goods and services sold to other countries (export) minus value of goods and services that foreigners sell us (Imports).

## Other Measures of Income

<center><h4>Gross National Product(GNP) = GDP + Factor Payments from Abroad - Factor Payments to Abroad</h4></center>

GNP measures the total income earned by nationals(residents of a nation)

<center><h4>Net national Product(NNP) = GNP - Depreciation </h4></center>

Depreciation of capital: the amount of the economy's stock of plants, equipment, and residential structures that wears out during the year.

<center><h4>Personal Income = National Income - Indirect Business Taxes - Corporate Profits - Social Insurance Contributions - Net Interest 
+ Dividends + Government Transfers to Individuals + Personal Interest Income </h4></center>

<center><h4> Disposable Personal Income = Personal Income - Personal Tax and Nontax Payments </h4></center>


# Measuring the Cost of Living: The Consumer Price Index (CPI)

## The Price of a Basket of Goods
__Consumer Price Index(CPI)__ turns the prices of many goods and services into a single index measuring the overall level of prices

<center><h4> CPI = $\frac{Prices of Baskets of Current Year}{Prices of Baskets of Base Year}$ </h4></center>

__CPI is a good measure to derive inflation as well as GDP Deflator. However, genearally, CPI overstates the inflation. We need to consider that when we use CPI__

# Measuring Joblessness: The Unemployment Rate
* Employed: those who at the time of the survey worked as paid employees, worked in their own business, or worked as unpaid workers in a family member's business.
* Unemployed: those who were not emplyed, were available for work, and had tried to find employment during the previous four weeks.
* Not in the labor force: those who fit neither of the first two categories, such as a full-time student, homemaker, or retiree.

<center><h4> Labor Force = Number of Employed + Number of Unemployed </h4></center>

<center><h4> Unemployment Rate = $\frac{Number of Unemployed}{Labor Force} \times 100$ </h4></center>

<center><h4> Labor-Force Participation Rate = $\frac{Labor Force}{Adult Population} \times 100$ </h4></center>

```{r}
Quandl.search("unemployment United States")
UE<-Quandl("FRBC/UNEMP_ST_US",type="xts")
plot(UE,type="l",main="Unemployment Rate of USA",xlab="year",ylab="Unemployment Rate")
plot(UE["2007::"],main="Unemployment Rate of USA",xlab="year",ylab="Unemployment Rate")
```